Обзор литературы по Tensor SSA

### 2025-04-02 TeX/master/papers_review.tex
cpd-based tssa review

\input{letters_series_mathbb}

@@

\section{Tensor SSA с использованием CPD}
\subsection{\href{https://doi.org/10.1109/tnsre.2014.2329557}{Tensor
    Based Singular Spectrum Analysis for Automatic Scor\-ing of Sleep
EEG}}\label{Kouchaki2015}
Рассматривается задача выделения одномерного вещественного сигнала
из ряда с нестационарным шумом.

@@

\subsection{\href{https://doi.org/10.3390/app7040418}{Improved
    Tensor-Based Singular Spectrum Analysis Based on Single Channel Blind
Source Separation Algorithm and Its Ap\-plication to Fault Diagnosis}}
\label{Yang2017}
Рассматривается задача выделения одномерного вещественного сигнала из ряда.

>>>>

\include{letters_series_mathbb}

@@

\section{Tensor SSA с использованием CPD}
\subsection{\href{https://doi.org/10.1109/tnsre.2014.2329557}{Tensor
    Based Singular Spectrum Analysis for Automatic Scoring of Sleep
EEG}}\label{Kouchaki2015}
Рассматривается задача выделения одномерного вещественного сигнала
из ряда с нестационарным шумом.

@@

\subsection{\href{https://doi.org/10.3390/app7040418}{Improved
    Tensor-Based Singular Spectrum Analysis Based on Single Channel Blind
Source Separation Algorithm and Its App\-lication to Fault Diagnosis}}
\label{Yang2017}
Рассматривается задача выделения одномерного вещественного сигнала из ряда.
